A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-14 FMCAD2021/1_intro.tex
intro: improvements & corrections

\wuhao{to do}

>>>>

The syntax of Presburger arithmetic with exponential functions (denoted by $\paexp$) in our setting is more natural and easy to understand. In the algorihm, Point's algorithm needs to transform the formula into DNF (disjunction normal form) before  eliminating any variables. In our algorithm, we assume no special form of the formula other than NNF (negation normal form). A sub-case of eliminating exponential terms in Point's algorithm is incorrect, we correct it in our lemma \ref{lem:exp-ineq} $a_i<0$ case.
